\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-28 paper.tex
Update on Overleaf.

\section{Application Example}
\label{application}

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language. \uwds's loose coupling allows for easy integration with the {\tt spatial_relations} between either an object recognition system that would allow for use in a physical environment(Figure~\ref{fig|l2torexample})

%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor} in order to conceptualise and visualise the spatial relations and visibility of the physical objects that participants interact with.

%In one of the scenarios of this project, participants are instructed by a NAO robot to manipulate a number of Duplo-like animals on top of a printed background paper which serves as a landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on pedagogical strategies to promote spatial relation learning by object manipulation. Such instructions include commands to place the elephant \textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside} the house.  To assess the performance, the robot and the operator need to compute spatial relationships between objects from the visual perspective of the participant.

>>>>

\section{Application Examples}
\label{application}

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language(l2). The loose coupling provided by \uwds allows for easy integration with the {\tt spatial\_relations} between either an object localisation system that would allow for use in a physical environment (Figure~\ref{fig|l2torexample}) or a virtual tablet game. As well this loose coupling facilitated development on multiple parts of the software individually across multiple international sites.

In the counting task the child is instructed to move toy animals into enclosures. The {\tt spatial\_relations} module calculates when the robots have been placed in the enclosure. The robot then teaches the children l2 words for the numbers and encourages the children to count along.

While teaching the spatial domain the

%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor} in order to conceptualise and visualise the spatial relations and visibility of the physical objects that participants interact with. In one of the scenarios of this project, participants are instructed by a NAO robot to manipulate a number of Duplo-like animals on top of a printed background paper which serves as a landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on pedagogical strategies to promote spatial relation learning by object manipulation. Such instructions include commands to place the elephant \textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside} the house.  To assess the performance, the robot and the operator need to compute spatial relationships between objects from the visual perspective of the participant.
